|

### 2021-02-10 appendix/appendix.Rmd
reorder factors desc stats, add age het fx exp02 exp03

\footnotesize
```{r race, warning=F, error=F, cache=T}
df1 %>%
  group_by(race) %>%
  filter(!is.na(race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "Other", "Rather Not Say", after = Inf)) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

As expected, our sample is also more educated than [the Brazilian
population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[5, 3]`%
have graduate school education.

\footnotesize
```{r education, warning=F, error=F, cache=T}
df1 %>%
  group_by(education) %>%
  filter(!is.na(education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Education = education) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Education") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r income, warning=F, error=F, cache=T}
df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Household Income") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r ideologytext, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology)
```

@@

\footnotesize
```{r ideology, warning=F, error=F, cache=T}
df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Political Ideology") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r death-penalty, warning=F, error=F, cache=T}
df1 %>%
  group_by(death_penalty) %>%
  filter(!is.na(death_penalty)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Support for Death Penalty` = death_penalty) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Support for Death Penalty") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r victimization, warning=F, error=F, cache=T}
df1 %>%
  group_by(previous_victim_dummy) %>%
  filter(!is.na(previous_victim_dummy)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Victimization = previous_victim_dummy) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Previous Victimization (12 Months)") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r police, warning=F, error=F, cache=T}
df1 %>%
  group_by(views_police) %>%
  filter(!is.na(views_police)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Opinion on the Police` = views_police) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Opinion on the Police") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r justice, warning=F, error=F, cache=T}
df1 %>%
  group_by(views_justice) %>%
  filter(!is.na(views_justice)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Opinion on the Judicial System` = views_justice) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Opinion on the Judicial System") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence our previous findings and confirm that
respondents select lynching victim profiles according to these two factors.
Criminal characteristics, such as age or race, do not seem to be particularly
relevant, as respondents do not mention them as much. The next words are
_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
(have to), and _justiça_ (justice). We believe these words correspond to cases
where respondents wanted to affirm they do not have any preference regarding
the lynching profiles, or that they would rather not have chosen any of the
alternatives.

@@

\footnotesize
```{r exp02-bart01, warning=F, error=F, message=F, cache=T}
df_exp02_het <- df_exp02 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"))

@@

@@

@@

@@

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp03main",
          title = "Experiment 03 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Constitution and penal code", "Human rights",
                               "Vendettas", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

\footnotesize
```{r exp03-bart01, warning=F, error=F, message=F, cache=T}
df_exp03_het <- df_exp03 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"))

@@

@@

@@

>>>>

\footnotesize
```{r race, warning=F, error=F, cache=T}
df1 %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "White", "Other", "Rather Not Say", after = Inf)) %>%
  group_by(Race) %>%
  filter(!is.na(Race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

As expected, our sample is also more educated than [the Brazilian
population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]*100`%
have graduate school education.

\footnotesize
```{r education, warning=F, error=F, cache=T}
df1 %>%
  rename(Education = education) %>%
  mutate(Education = fct_relevel(Education, "Primary School", "Secondary School",
                                 "High School", "College", "Graduate School")) %>%
  group_by(Education) %>%
  filter(!is.na(Education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Education") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r income, warning=F, error=F, cache=T}
df1 %>%
  rename(`Household Income` = household_income) %>%
  mutate(`Household Income` = fct_relevel(`Household Income`, "Up to R$1,000",
                                          "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                          "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                          "From R$10,001 to R$20,000", "Above R$20,000")) %>%
  group_by(`Household Income`) %>%
  filter(!is.na(`Household Income`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Household Income") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r ideologytext, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  mutate(ideology = fct_relevel(ideology, "Left")) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology)
```

@@

\footnotesize
```{r ideology, warning=F, error=F, cache=T}
df1 %>%
  rename(Ideology = ideology) %>%
  mutate(Ideology = fct_relevel(Ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right")) %>%
  group_by(Ideology) %>%
  filter(!is.na(Ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Political Ideology") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r death-penalty, warning=F, error=F, cache=T}
df1 %>%
  rename(`Support for Death Penalty` = death_penalty) %>%
  mutate(`Support for Death Penalty` = fct_relevel(`Support for Death Penalty`, "Yes", "No")) %>%
  group_by(`Support for Death Penalty`) %>%
  filter(!is.na(`Support for Death Penalty`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Support for Death Penalty") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r victimization, warning=F, error=F, cache=T}
df1 %>%
  rename(Victimization = previous_victim_dummy) %>%
  mutate(Victimization = fct_relevel(Victimization, "Yes", "No")) %>%
  group_by(Victimization) %>%
  filter(!is.na(Victimization)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Previous Victimization (12 Months)") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r police, warning=F, error=F, cache=T}
df1 %>%
  rename(`Opinion on the Police` = views_police) %>%
  mutate(`Opinion on the Police` = fct_relevel(`Opinion on the Police`, "Very Good", "Good",
                                               "Regular", "Bad", "Very Bad")) %>%
  group_by(`Opinion on the Police`) %>%
  filter(!is.na(`Opinion on the Police`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Police") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r justice, warning=F, error=F, cache=T}
df1 %>%
  rename(`Opinion on the Justice System` = views_justice) %>%
  mutate(`Opinion on the Justice System` = fct_relevel(`Opinion on the Justice System`, "Very Good",
                                                       "Good", "Regular", "Bad", "Very Bad")) %>%
  group_by(`Opinion on the Justice System`) %>%
  filter(!is.na(`Opinion on the Justice System`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Justice System") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence our previous findings and confirm that
respondents select lynching victim profiles according to these two factors.
Criminal characteristics, such as age or race, do not seem to be particularly
relevant, as respondents do not mention them as much. The following terms are
_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
(have to), and _justiça_ (justice). We believe these words correspond to cases
where respondents wanted to affirm they do not have any preference regarding
the lynching profiles, or that they would rather not have chosen any of the
alternatives.

@@

\footnotesize
```{r exp02-bart01, warning=F, error=F, message=F, cache=T}
df_exp02_het <- df_exp02 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))

@@

# Age
summary(bartc(exp02_outcomes, exp02_police_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

@@

# Age
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

@@

# Age
df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(age2)
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp02_small_punishment2,
              n.chains = 5L, seed = 144))

@@

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE, align = TRUE,
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Constitution and penal code", "Human rights",
                               "Vendettas", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

\footnotesize
```{r exp03-bart01, warning=F, error=F, message=F, cache=T}
df_exp03_het <- df_exp03 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))

@@

# Age
df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(age2)
summary(bartc(exp03_outcomes, exp03_constitution_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp03_constitution2,
              n.chains = 5L, seed = 144))

@@

# Age
df_exp03_rights2 <- df_exp03_rights %>% drop_na(age2)
summary(bartc(exp03_outcomes, exp03_rights_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp03_rights2,
              n.chains = 5L, seed = 144))

@@

# Age
df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(age2)
summary(bartc(exp03_outcomes, exp03_vendetta_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp03_vendetta2,
              n.chains = 5L, seed = 144))
